\vspace{-13mm}\includegraphics[width=15mm,scale=3]{../images/IST_Logo.png} \\ {\fontsize{24}{16}Detection of Li in Technological Materials through Nuclear Reactions} \vspace{-5mm}

### 2024-01-19 text/paper/paper.tex
CURVO
VAI

It is evident that the structure of the spectrum follows a similar pattern to the one in the previous sample.
First, there is electrical noise, followed by backscattering and event pile-up. 
The backscattering is identified by the barrier of 1150.0 kEv.

@@

>>>>

It is evident that the structure of the spectrum follows a similar pattern to the one in the previous sample.
First, there is electrical noise, followed by backscattering and event pile-up. 
The backscattering is identified by the barrier of 1150.0 kEv.
Finally, there is the lithium peak, which has an energy profile as well due to the depth of the sample.

@@

Just like before, there is electrical noise, followed by backscattering and event pile-up.
However, this sample is implanted only on the surface, therefore there is no energy profile as expected, since the lithium isn't being detected at different depths.
